Combined Task and Motion Planner through an Interface Layer

### 2015-04-13 documentation/draft.tex
fixed move back angle

An alternative approach to developing an interface between the task and motion planner is for the task planner to discretize the geometric state space. However, the number of required discretizations to solve the problem is generally very large and results in extremely large or infeasible problems. The interface allows the task planner state space to use an abstract state space which ignores geometry. The interface layer translates geometric constraints and passes them to the task planner.
\section{Problem Statement}

\section{High Level Approach}

>>>>

An alternative approach to developing an interface between the task and motion planner is for the task planner to discretize the geometric state space. However, the number of required discretizations to solve the problem is generally very large and results in extremely large or infeasible problems. The interface allows the task planner state space to use an abstract state space which ignores geometry. The interface layer translates geometric constraints and passes them to the task planner.

\section{Problem Statement}

We implemented an interface between a task and motion planner for the Baxter robot designed by Rethink Robotics. For the motion planner we used OMPL from the ROS move-it interface and FF for our task planner. We instructed Baxter to pickup and place cylinders standing on a table. The cylinders were placed such that Baxter could not reach all of the cylinders in the initial state.

\section{High Level Approach}
We implemented wrappers to incorporate the motion and task planners with the interface API. The interface layer
